Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r alphabeta alpha}
plot.alpha <- function(diversity,  width = .4, posdodge = .25, aspectratio = 2, colorlimit = 0.25) {
    plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                             values = rescale(c(-amaxb,-0.1, 0, 0.1, colorlimit)),
                             name = 'Regression coefficient \nin linear model \nfor Shannon index',
                             limits = c(-1.05*amaxb, 1.05*amaxb),
                             na.value = "black") +
        theme_classic(20) +
        geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
        scale_shape_manual(name="",
                           values=c('*'='*', ' '=' '),
                           labels=c("*"="significant at FDR 0.05", ' '=' '),
                           breaks=c("*", ' ')) +
        xlab("") +
        ylab("") +
        theme(legend.position="right",
              legend.title=element_text(size = 14),
              legend.direction="vertical",
              legend.text=element_text(size = floor(0.75*20)),
              legend.box.margin=margin(t = 1, unit = "cm"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              axis.line.y = element_line(linetype="blank"),
              axis.line.x = element_line(linetype="blank"),
              legend.title.align = 0,
              legend.text.align = 0,
              axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"))+
        scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

@@

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(1,    2,    3, NA, NA),
                      c(1,    2,    3, NA, 4),
                      c(NA, 5,    6, NA, NA),
                      c(NA, NA, 7, NA, NA)),
                  widths=c(4, 0.7, 5, 0.7, 3),
            heights=c(3, 7, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)

>>>>

```{r alphabeta alpha}
plot.alpha <- function(diversity,  width = .4, posdodge = .25, aspectratio = 2, colorlimit = 0.25) {
    plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                             values = rescale(c(-colorlimit, 0, colorlimit)),
                             name = 'Regression coefficient \nin linear model \nfor Shannon index',
                             limits = c(-colorlimit, colorlimit),
                             na.value = "black") +
        theme_classic(20) +
        geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
        scale_shape_manual(name="",
                           values=c('*'='*', ' '=' '),
                           labels=c("*"="significant at FDR 0.05", ' '=' '),
                           breaks=c("*", ' ')) +
        xlab("") +
        ylab("") +
        theme(legend.position="right",
              legend.title=element_text(size = 14),
              legend.direction="vertical",
              legend.text=element_text(size = floor(0.75*20)),
              legend.box.margin=margin(t = 0, unit = "cm"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              axis.line.y = element_line(linetype="blank"),
              axis.line.x = element_line(linetype="blank"),
              legend.title.align = 0,
              legend.text.align = 0,
              axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"))+
        scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

@@

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(4,    2,    3, NA, NA),
                      c(1,    2,    3, NA, NA),
                      c(NA, 5,    6, NA, NA),
                      c(NA, NA, 7, NA, NA)),
                  widths=c(4, 0.7, 5, 0.7, 4),
            heights=c(3, 7, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)

### 2019-01-25 rrbiome.Rmd
Minor

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
```

@@

```{r matrix calculation, cache = FALSE}
if (!file.exists("rds/bray.dist.m.species.rds") || !file.exists("rds/bray.dist.m.genus.rds")) {
    bray.dist.m.species <- calculate.beta.matrix(pseq.species)
    saveRDS(bray.dist.m.species, file = "rds/bray.dist.m.species.rds")
    bray.dist.m.genus <- calculate.beta.matrix(pseq.genus)
    saveRDS(bray.dist.m.genus, file = "rds/bray.dist.m.genus.rds")
} else {
    bray.dist.m.species  <- readRDS("rds/bray.dist.m.species.rds")
    bray.dist.m.genus <- readRDS("rds/bray.dist.m.genus.rds")
}
```

@@

 ```{r adonis calculation, cache = FALSE}
if (!file.exists("rds/adonis.species.rds")) {
    adonis.species <- calculateadonis(dset = meta(pseq.species),
                                      matrix = bray.dist.m.species,
                                      covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                      npermutations = 99)
    saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
```

@@

```{r matrix calculation}
if (!file.exists("rds/bray.dist.m.species.rds") || !file.exists("rds/bray.dist.m.genus.rds")) {
    bray.dist.m.species <- calculate.beta.matrix(pseq.species)
    saveRDS(bray.dist.m.species, file = "rds/bray.dist.m.species.rds")
} else {
    bray.dist.m.species  <- readRDS("rds/bray.dist.m.species.rds")
}
```

@@

 ```{r adonis calculation}
 if (!file.exists("rds/adonis.species.rds")) {

     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 99)

     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 99)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```
